
\section{Debugging Support}

Some environment variable settings may help debugging PiP programs.

\subsection{\PIPKW{PIP_STOP_ON_START}}

This environment variable is to stop (by sending {\tt SIGSTOP} to
spawned PiP task just before calling the \pipterm{before hook}
(Section~\ref{sec:hooks}), or jumping to the starting function if
before hook is not given. The value of this environment must meet the
following format;  

\begin{lstlisting}[frame=tb]
  PIP_STOP_START=[<script-file>]@<PIPID>
\end{lstlisting}

The optional {\tt\option{script}} is a shell
script to be executed on the suspension, and {\tt\option{PIPID}} is the
\PIPID\ to be suspended. If {\tt\option{PIPID}} is -1, then all spawned PiP
tasks will be stopped. The {\tt\option{script}} is invoked with
three parameters; PID and \PIPID\ of the stopped PiP task, followed by a
path to the program of the task. Do not forget to set the {\it
  executable} bit on this {\tt\option{script-file}} file.

\lstinputlisting[style=program,
  caption={Stop-on-start Script Example},
  label=prg:stop-on-start] {debug/examples/onstart.cmd}

Listing~\ref{prg:stop-on-start} shows an example of the script for the
\pipenv{PIP_STOP_ON_START}. Here, \pipcomm{pips} command is invoked
instead of some debugging command\footnote{All examples are executed
on a Docker environment but {\tt ptrace} (and other commands using
{\tt ptrace}) was unable to run in this example even withthe {\tt
  --cap-add=SYS_PTRACE} Docker option (I confirmed {\tt gdb} worked). So 
\pipcomm{pips} was used instead in this example.}. Note that 
the target task is already stopped by delivering the {\tt SIGSTOP}
signal. Somehow you have to explicitly deliver the {\tt SIGCONT}
signal to the task if you want to resume the
task. Listing~\ref{out:stop-on-start} shows the result of 
\pipenv{PIP_STOP_ON_START} execution with this script file. 

\lstinputlisting[style=example, basicstyle=\tiny\tt, 
  caption={Stop-on-start Script Example - Execution},
  label=out:stop-on-start] {debug/examples/stop-on-start.out}

\subsection{\PIPKW{PIP_GDB_SIGNALS}}

This environment variable \pipenv{PIP_GDB_SIGNALS} is to set the
signals to trigger some actions by specifying the
\pipenv{PIP_SHOW_MAPS} and \pipenv{PIP_SHOW_PIPS}, followed by
the PiP-gdb invocation. The value of this environment is as follows;

\begin{lstlisting}[frame=tb]
  PIP_GDB_SIGNALS=[ <SIGNAME> ] { "+"|"-" <SIGNAME> }
\end{lstlisting}

The possible {\tt\option{SIGNAME}} vale are listed below;

\begin{table}[ht]
  \centering
  \caption{Possible Signal Names for \pipenv{PIP_GDB_SIGNALS}}
  \vspace{3mm}
  \tt
  \begin{tabular}{l}
    SIGHUP \\
    SIGINT \\
    SIGQUIT \\
    SIGILL \\
    SIGABRT \\
    SIGFPE \\
    SIGINT \\
    SIGSEGV \\
    SIGPIPE \\
    SIGUSR1 \\
    SIGUSR2 \\
    ALL \\
  \end{tabular}
\end{table}

Here, {\tt ``ALL''} means all signals list in this table. Each signal
name in this table can be concatenated by using the plus (+) and/or
minus (-) symbols.  For example, ``{\tt ALL-SIGUSR1}'' indicates the
all signals excluding {\tt SIGUSR1}. ``{\tt SIGUSR1+SIGUSR2+SIGINT}''
represents {\tt SIGUSR1}, {\tt SIGUSR2} and {\tt SIGINT}. 

\subsection{\PIPKW{PIP_SHOW_MAPS}}

If \pipenv{PIP_SHOW_MAPS} environment is set to ``{\tt on}'' and the
a signal specified by the \pipenv{PIP_GDB_SIGNALS} is delivered, then
the address map (Listing~\ref{out:maps}, for example) will be shown. 

\subsection{\PIPKW{PIP_SHOW_PIPS}}

If \pipenv{PIP_SHOW_PIPS} environment is set to ``{\tt on}'' and the
a signal specified by the \pipenv{PIP_GDB_SIGNALS} is delivered, then
\pipcomm{pips} command (Section~\ref{sec:pips}) is invoked to show the
status of the other PiP tasks in the same address space.

\subsection{\PIPKW{PIP_GDB_PATH} and \PIPKW{PIP_GDB_COMMAND}}

When \pipenv{PIP_GDB_PATH} is set to the path to \pipcomm{pip-gdb}
a signal specified by the \pipenv{PIP_GDB_SIGNALS} is delivered, then
PiP gdb (Section~\ref{sec:pip-gdb}) will be invoked. If the value of
the \pipenv{PIP_GDB_COMMAND} environment is set to a valid filename
and if the filename contains some GDB commands, then PiP-gdb will be
invoked to work with this command file. 
